Clustering exploration for `r params$library_id`

### 2024-12-17 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering-metrics.Rmd

>>>>

Before we show any statistics, we will first show the number of clusters for each set of parameters. 
For any cases where we only see 1 cluster, no distributions will be shown in the plots.

```{r}
all_stats |> 
  purrr::imap(\(df, method){
    df |> 
      dplyr::select(resolution, nn, cluster) |> 
      dplyr::group_by(resolution, nn) |> 
      dplyr::summarise(num_of_clusters = length(unique(cluster))) |>
      knitr::kable()
  })
```
